First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-06-08 eg6-letters/coherent/dvcs_he4_prl.tex
Acknowlegments updated.

%Acknowledgments

We acknowledge the staff of the Accelerator and Physics Divisions at Jefferson 
Lab for making this experiment possible.

Dave Ireland- the United Kingdom's Science and Technology Facilities Council

Lamiaa- the Physics and Astronomy Department and the Office of Research and 
Economic Development at Mississippi State University, and the US Department of 
Energy Award DE-FG02-07ER41528.

Kim- The National Research Foundation of Korea

- This work is supported by the U.S.  Department of Energy, Office of Science, 
Office of Nuclear Physics, under contracts DE-AC02-06CH11357 and 
DE-AC05-06OR23177.

>>>>

%Acknowledgments
The authors thank the staff of the Accelerator and Physics Divisions at the 
Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional 
de Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), the Italian 
Instituto Nazionale di Fisica Nucleare, the French Centre National de la 
Recherche Scientifique, the French Commissariat \`a l'Energie Atomique, the 
U.S. Department of Energy, the UK Science and Technology Facilities Council 
(STFC), the Scottish Universities Physics Alliance (SUPA), the National 
Research Foundation of Korea, and the Office of Research and Economic 
Development at Mississippi State University.  The author (M.~Hattawy) also 
acknowledge the support of the Consulat G\'en\'eral de France \`a J\'erusalem. 
The Southeastern Universities Research Association operates the Thomas 
Jefferson National Accelerator Facility for the United States Department of 
Energy under contract DE-AC05-06OR23177.
